BOAST: a Metaprogramming Framework to Produce Portable and Efficient Computing Kernels for HPC Applications

### 2014-07-31 Paper/BOAST.tex
updated paper

@@

>>>>

    \subsubsection{BOAST keywords}

  In order to clearly differentiate what is going to be generated from what is
related to manipulations in the host language the \emph{print} method was
redefined in the BOAST namespace. This print method only insures that the object
it is called on implements a public print method. Each BOAST object is
responsible for printing itself correctly depending on the BOAST configuration
at the time the print public method is called.

    \subsubsection{BOAST Abstractions}

  Variable

  Expression

  If

  For

  While

  Case

@@

  POET
